Sea: A hierarchical filesystem for Big-Data Scientific Computing

### 2021-06-16 paper/paper.tex
added paper updates

\documentclass[10pt,journal,compsoc]{IEEEtran}

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{E}{ffecient} data-management strategies have become imperative in 
mitigating the costs of processing large datasets. These strategies come in the form
of data locality, which ensures that computation is performed where the data resides
rather than relocating the data, and in-memory computing, which ensures that the data is
maintained in RAM, whenever possible. Big Data frameworks, such as the Hadoop MapReduce, Spark and Dask,
have evolved to support either or both of these strategies.
However, while many domains have adopted the use of Big Data framework and filesystems to ensure effective data
management within their applications, many scientific applications are developed without such strategies in mind.
% add speedup results

Scientific applications may omit leveraging Big Data frameworks, despite having Big Data workloads,
for many reasons. One such reason may be the data format. BigData frameworks were originally developed
for text-processing. Scientific applications, in contrast, may rely on image processing for their
analyses. The fundamental differences between these two data formats made leveraging BigData frameworks for
scientific image processing non-trivial. While recent efforts have been made to support data-intensive
image processing workloads, there remains some work to be done.

Scientific applications are usually composed of numerous well-established command-line tools. These tools
may have been developed at a time when the processing would have been compute intensive, thus not requiring any
data management strategies, yet remain scientifically relevant. While newer applications
that leverage such tools may be written using Big Data frameworks, such frameworks are not designed to transfer
data in-memory to command-line applications, and thus would require some instrumentation.

While various infrastructures are available to researchers, including local workstations, cloud and 
High Performance Computing (HPC) clusters, researchers commonly rely on HPC clusters due to their low cost and available
resources. Such clusters typically rely on a network-based parallel file system, such as Lustre, Ceph and GlusterFS.
Since data storage and compute are maintained as separate entities on HPC clusters, processing BigData workflows on them
may be particularly costly, particularly when no BigData framework is applied. Furthermore, while it is possible to execute
workloads using BigData frameworks on HPC, these frameworks are typically incompatible with the native resource managers (e.g. SLURM, PBS),
and therefore, and overlay cluster must be used.

@@

@@

% add related work section
\section{Related Work}
\subsection{Lustre}
% change lustre to shared filesystem
\subsubsection{Other Luster optimizations}
\subsection{Big Data Frameworks and File systems}
HDFS Alluxio Hadoop Spark Dask
\subsubsection{What are they/how do they work}
\subsubsection{Why are the suboptimal for neuroimaging/on HPC}
\subsection{The linux page cache}
\subsubsection{What is it/how does it work}
\subsubsection{Why do we still need Sea}
\subsection{File System implementations}
\subsubsection{Kernel-space file systems}
\subsubsection{Burst Buffers}
\subsubsection{Unionfs}
\subsubsection{FUSE}
\subsubsection{System call interception with ptrace}
\subsubsection{LD\_PRELOAD}
xtreemfs/xtreemos

@@

\subsection{Sea design and implementation}
\subsubsection{Overview}

Sea is a C++ library that redirects files written to a user-specified mount point, to the
appropriate storage devices. It achieves this through the interception of libc calls using
the LD\_PRELOAD functionality. Within an intercepted call the file will be written to or read
from the best available storage device. At minimum, a user must specify at least two storage devices, a fast
temporary one and a slower long-term storage one. This could be RAM and SSD if working on a single node, or a compute-local SSD
and a shared parallel file system, in the case of an HPC cluster. Ideally, a user will provide a multitude of short-term storage
devices to improve Sea's efficacy. Furthermore, to maximize usage of the fastest available
storage devices, Sea will allow the user to outline which files can be removed from short-term storage in addition
to which files need to be materialized onto long-term storage.

@@

Sea is primarily designed to work with workloads that generate copious amount of intermediate data.
Since data must be read from the slower storage device and final output data most likely would have to
be written to the same device, the use of Sea with workloads that do not produce intermediate data would
bring no speedup and may introduce some overheads.

Sea provides two main modes, that are dictated by how the user specifies flushing and eviction: In-memory computing and flush-all.
In-memory computing is achieved when intermediate need not be materialized to long-term storage. In these scenarios, Sea can fully
leverage local (short-term) storage performance to maximize performance. This can be coupled with eviction to limit the amount of
data that will be written to slower, but larger local storage devices. With Sea in memory, we can expect performance comparable to
that of using BigData frameworks.

Occasionally, it is desired to materialize even intermediate data to long-term storage devices, for potential future use. The
performance gain from using Sea in these scenarios, however, is largely bounded by data size. In the instance where the workloads is more compute intensive,
we can gain speedup by masking all or part of the I/O through long-term storage by executing the flush during a compute task. In data-intensive scenarios, the 
opposite can be seen: compute time can be masked by I/O (add figure + model). Despite the performance gain being limited in
such a scenario, a performance gain can still be observed through the use of Sea.

@@

In order to redirect data to different filesystems, Sea uses LD\_PRELOAD to intercept libc calls. Depending on the
version of libc used, function calls may differ. Sea is currently compatible with libc version X-X.

@@

\subsubsection{Flushing and eviction}
There are four different available usage scenarios: flush, evict, flush and evict and do nothing.
A flush operation represents a copy operation that duplicates the data located on short-term storage to long-term storage.
In contrast, an evict represents a rm. That is 
\subsubsection{Configuration File}
\subsubsection{Program execution}
\subsubsection{Limitations}
behaviour unspecified in mixed static/dynamic workloads

\subsection{Experiments}
\subsubsection{Infrastructure}
\subsubsection{Pipelines}
Big Brain incrementation
fmri processing?

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{longtable}
\usepackage[binary-units=true]{siunitx}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amsmath}

\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
\algblock{Input}{EndInput}
\algnotext{EndInput}
\algblock{Output}{EndOutput}
\algnotext{EndOutput}
\newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}: #1}}}

% benchmark on beluga, prefreesurfer with RUIS
% use more than 64 subjects for prefreesurfer --> few 100 subjects
% think more about how to benchmark I/O
% try distributed jobs with Sea

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{E}{fficient} data-management strategies have become essential in 
mitigating the costs of Big Data processing. These strategies come in the form
of data locality, which ensures that computation is performed where the data resides
rather than relocating the data, and in-memory computing, which ensures that the data is
maintained in RAM, whenever possible. These strategies are built-into popular Big Data Frameworks
such as Hadoop MapReduce~\cite{mapreduce}, Spark~\cite{spark} and Dask~\cite{dask}.
Despite recent widespread adoption of Big Data frameworks and filesystems to ensure effective data
management within applications, many widely-used scientific applications forgo such optimization for various reasons.
Sea aims to enable Big Data optimization performance to existing scientific applications without reinstrumentation.
% add speedup results

Many scientific applications, such as those found in geography and neuroscience, perform
image processing. However,  BigData frameworks were originally developed
for text-processing and have only recently incorporated components that could facilitate
the processing of images. The fundamental differences between these two data formats make leveraging
BigData frameworks for
scientific image processing non-trivial, even considering recent advances.

Scientific applications are usually composed of numerous well-established command-line tools. These tools
may have been developed at a time when processing would have been compute intensive, thus do not incorporate
data management strategies. While newer applications
that leverage such tools may be written using Big Data frameworks, such frameworks are not designed to transfer
data in-memory to command-line applications, making it difficult to incorporate these tools without additional
overhead.

Although various infrastructures are available to researchers, such as local workstations, the cloud (AWS, ..etc) and 
High Performance Computing (HPC) clusters, researchers commonly rely on HPC clusters due to their low cost and available
resources. Such clusters typically rely on a network-based parallel file system, such as Lustre, Ceph and GlusterFS.
Since data storage and compute are maintained as separate entities on HPC clusters, processing BigData workflows on them
may be particularly costly, particularly when no BigData framework is applied. Furthermore, while it is possible to execute
workloads using BigData frameworks on HPC, these frameworks are typically incompatible with the native resource managers (e.g. SLURM, PBS),
and therefore, and overlay cluster must be used.

@@

%multiple disk support
% pipeline agnostic and pipeline access patterns
% don't leverage workflows
% leverage existing filesystems
% replace storage devices with storage location.
% use applications
% memory management paragraph: PAGE CACHE
% shared filesystems are slow and metadata management can be slow

@@

% add related work section
\section{Related Work}
\subsection{HPC Infrastructure}
      The general structure of HPC clusters may complicate the deployment of Big Data frameworks.
      Typical HPC clusters consist of distinct storage and compute nodes. While the compute
      nodes may also have local storage, there is no distributed file system like HDFS or
      Alluxio to facilitate data locality. Furthermore, access to these compute nodes is
      temporary, with allocation duration enforced by a batch scheduler. Therefore, any
      data written to a compute node is inaccessible after the allocation is terminated.

      The storage layer found on HPC clusters consists of a high-performance parallel
      distributed file system such as Lustre~\cite{lustre}. This file system is made
      accessible to every compute node within the cluster, connected to each node via
      high-performance network interconnect such as InfiniBand~\cite{infiniband}. Although
      it is a high performance network, it nevertheless can be a source of bottlenecks as
      the network is shared between all users on the cluster. Furthermore, there are
      additional overheads that can be incurred. In the case of Lustre,
      there are many data nodes, known as Object Storage Servers (OSS) which contain
      several storage devices, known as Object Storage Targets (OST). All file metadata
      is maintained within a separate node known as the Metadata Server (MDS) and stored within
      a device referred to as the Metadata Target (MDT). Although data transfers can be
      communicated directly to the corresponding OST, the clients need to first communicate
      with the MDS to determine which OST to communicate with. This can result
      in data transfer overheads, particularly when making numerous requests to the metadata server.
      Occasionally, HPC clusters provide a faster intermediate storage layer, known as a Burst Buffer,
      which can improve the overall performance of I/O operations to Lustre.

      \subsubsection{Burst Buffers}

\subsection{Big Data Frameworks and File systems}

      Strategies to facilitate the processing of such large datasets is required. In text-based
      processing, frameworks such as MapReduce~\cite{mapreduce} and Apache Spark~\cite{spark}
      have implemented and popularized strategies to minimize the need for data transfers during processing.
      These strategies are known as data locality and in-memory computing.

      Data locality is the process by which compute tasks are scheduled nearest to where
      the data is located. Traditionally, storage and compute were kept separate,
      having to transfer data over the network to compute. Rather than having to transfer large amounts of data over the
      network to the compute tasks, which could incur significant overheads, Big Data frameworks ensure that data is
      stored directly on the compute nodes. When a compute task requires access to specific
      data, the scheduler sends the task to the nearest available node to the data, thereby
      minimizing any cost of network-related data transfers. This strategy is not only
      used by Big Data Frameworks such as Hadoop MapReduce, Apache Spark, and Dask~\cite{dask},
      but also enabled by file systems such as the Hadoop Distributed File System (HDFS)~\cite{hdfs}
      and Alluxio~\cite{alluxio}.

\subsection{The linux page cache}
 While scientific applications uncommonly use Big Data frameworks and must perform
      large over-the-network data transfers, they may still benefit from in-memory
      computing and data locality through the Linux Page Cache~\cite{pagecache}. Similarly to other
      filesystems, Lustre leverages the client node page cache to reduce I/O overheads.
      System memory is composed of two components: 1) anonymous memory and 2) page cache.
      Anonymous memory consists of all application-related objects, whereas page cache
      consists of recently accessed file data. When a file is read, that file is loaded
      up into the page cache to be flagged for eviction based on a least recently used (LRU)
      policy. That means subsequent accesses to that data may be done entirely
      in memory so long as that data has not already been evicted. Similarly, for writes
      to a file system with writeback cache enable, the file will be written to memory
      completing the write operation once the file has been written entirely to memory.
      That file will then be flushed asynchronously to the appropriate storage device.
      As system memory may get overloaded with too many write requests, there is a limit to the amount of written data that
      can exist in memory, known as the \texttt{dirtyi\_ratio}. Furthermore, applications
      producing too many write requests may be throttled by the system.
\subsection{File System implementations}
      Due to the architecture of conventional HPC clusters, network based parallel
      files systems are favoured over Big Data distributed filesystems. Such filesystems
      require super user access, preventing users from deploying their own own on-the-fly cluster.
      While HDFS can be loaded in user-space by mounting its File System in Userspace (FUSE) implementation,
      FUSE-based filesystems can perform significantly worse than desired, depending on the application~\cite{tofuse}.
      Even with a userspace version of HDFS, there would
      be no mechanism to transfer all the data back to the parallel filesystem to be accessible
      post resource requests. Furthermore, such filesystems are not POSIX-compliant, which
      would be required for scientific computing applications.

      There are, however, BigData filesystems, such as XtreemFS~\cite{xtreemfs} that
      exist entirely within user space, are POSIX-compliant, and can use alternative
      methods to FUSE to function. XtreemFS leverages libc interception using the LD\_PRELOAD
      trick to intercept filesystem calls made to the libc library. There are
      limitations to using libc interception, such as there needs to be libc call to intercept and the
      application making the calls must be dynamically linked.
      There are alternatives to libc intercept that can bypass these issues, such as
      system call interception, but they have greater overheads as compared to libc interception~\cite{quinson}.
      Furthermore, most applications are dynamically linked and use libc to interact
      with the filesystem. Characteristics that make XtreemFS unlikely to be deployed
      on-the-fly include complex filesytem deployment and configuration properties. It
      also does not provide a simple way to leverage different classes of storage
      devices, nor ensure that required data will be copied to the cluster's parallel file system.
      %include triple-H
%\subsubsection{Kernel-space file systems} add comments in methods
\subsubsection{Unionfs}
\subsubsection{FUSE}
% add number w/o plot
\subsubsection{System call interception with ptrace}
\subsubsection{LD\_PRELOAD}
xtreemfs/xtreemos

@@

\subsection{Sea design and implementation}
\subsubsection{Overview}
\todo{mention that it's unix compatible}
Sea is a Linux-compatible C++ library that redirects files accessed from a user-specified mount point to the
appropriate storage devices. In order to effectively redirect all data transfers, it leverages the LIBC\_PRELOAD functionality which
enables the interception of libc calls. Within an intercepted call the file will be written to or read
from the best available storage device. At minimum, a user must specify at least two storage devices, a fast
temporary one and a slower long-term storage one. This could be RAM and SSD if working on a single node, or a compute-local SSD
and a shared parallel file system, in the case of an HPC cluster. Ideally, a user will provide a multitude of short-term storage
devices to improve Sea's efficacy. Furthermore, to maximize usage of the fastest available
storage devices, Sea will allow the user to outline which files can be removed from short-term storage in addition
to which files need to be materialized onto long-term storage.

@@

Sea is primarily designed to work with workloads that generate copious amount of intermediate data.
Since data must be read from the slower storage device and final output data most likely would have to
be written to the same device, the use of Sea with workloads that do not produce intermediate data would
bring no speedup and may even introduce some overheads.

Sea provides two main modes that are dictated by how the user specifies flushing and eviction: In-memory computing and flush-all.
In-memory computing is achieved when intermediate need not be materialized to long-term storage. In these scenarios, Sea can fully
leverage local (short-term) storage to maximize performance. This can be coupled with eviction to limit the amount of
data that will be written to slower, but larger local storage devices. With Sea in memory, we can expect performance comparable to
that of using BigData frameworks.

Occasionally, it is desired to materialize even intermediate data to long-term storage devices, for potential future use. The
performance gain from using Sea in these scenarios, however, is largely bounded by data size. In the instances where the workloads is more compute intensive,
we can gain speedup by masking all or part of the I/O through long-term storage by executing the flush during a compute task. In data-intensive scenarios, the 
opposite can be seen: compute time can be masked by I/O (add figure + model). Despite the performance gain being limited in
such a scenario, a performance gain can still be observed through the use of Sea.

@@

Depending on the version of libc used, function calls may differ. Sea is currently compatible with libc version X-X.
\todo{depending on the version of libc, the application static/dynamic linking, version of the function}

@@

Sea currently does not support the partitioning of files across multiple devices. Since it cannot predict the size of the outputs to ensure the
existence of sufficient space on storage devices, the user must provide within the Sea configuration file the maximum file size produced by the workflow.
Together with the specified amount of parallel processes, Sea calculates the minimum space required on a storage device to write the file to it \todo{should include an equation here}.
Sea will then go through the hierarchy of available storage devices an select the fastest storage device with sufficient available space.

While this process may result in not utilizing all available space in fast storage devices, it will still allow users to gain a performance speedup on the pipeline given that the
number of threads multiplied by the file size does not exceed storage space.

\todo{minimum storage size calculations is thread-safe}
\todo{talk about testing}

\subsubsection{Flushing and eviction}
\todo{add diagrams here?}
There are four different available usage scenarios: flush, evict, flush and evict and do nothing.
A Sea flush is synonymous to a file copy in that files that are stored within Sea but have not yet been materialized
to the long-term storage device will be copied to long-term storage. Flushing generally required for all intermediate data
that are required for future analysis.

Eviction, on the other hand, depicts a remove operation. Any file that is evicted from Sea will be removed from any of the storage mount
points located in Sea.

\subsubsection{Configuration File}
\subsubsection{Program execution}
\subsubsection{Limitations}
behaviour unspecified in mixed static/dynamic workloads

\subsection{The Sea and Lustre model}\label{model}

      \begin{table}
      \centering
      \begin{tabular}{|p{0.05\linewidth}|p{0.6\linewidth}|p{0.1\linewidth}|}
       \hline
       \multicolumn{3}{|c|}{Makespans} \\
       \hline
       $M_{n}$ & I/O to storage device level $n$ & Eq.~\ref{eq:sea}\\
       $M_{l}$ & I/O to Lustre w/o page cache & Eq.~\ref{eq:lustrenpc}\\
       $M_{c}$ & I/O to page cache & Eq.~\ref{eq:cache}, \ref{eq:lustrepc}, \ref{eq:sea}\\
       $M_{lc}$ & I/O to Lustre w/ page cache & Eq.~\ref{eq:lustrepc}\\
       $M_{s}$ &  I/O to Sea w/o page cache & Eq.~\ref{eq:sea}\\
       $M_{sl}$ & I/O to the Lustre component of Sea & Eq.~\ref{eq:snc}, \ref{eq:msl} \\
       $M_{sd}$ & I/O to the local disk component of Sea & Eq.~\ref{eq:snc}, \ref{eq:msd} \\
       $M_{st}$ & I/O to the tmpfs component of Sea & Eq.~\ref{eq:snc}, \ref{eq:mst} \\
       $M_{sc}$ & I/O to Sea with page cache & Eq.~\ref{eq:msc} \\
       \hline
       \multicolumn{3}{|c|}{Data size} \\
       \hline
       $D_{r}$ & Read data & Eq.~\ref{eq:lustrenpc}\\
       $D_{w}$ & Written data & Eq.~\ref{eq:lustrenpc}\\
       $D_{cr}$ & Cached read data & Eq.~\ref{eq:cache}\\
       $D_{cw}$ & Cached written data & Eq.~\ref{eq:cache}\\
       $D_{I}$ & Input data & Eq.~\ref{eq:lustrepc}, \ref{eq:sea}\\
       $D_{tr}$ & Sea: tmpfs read data & Eq.~\ref{eq:mst} \\
       $D_{tw}$ & Sea: tmpfs written data & Eq.~\ref{eq:mst} \\
       $D_{dr}$ & Sea: local disk read data & Eq.~\ref{eq:msd} \\
       $D_{dw}$ & Sea: local disk written data & Eq.~\ref{eq:msd} \\
       $D_{lr}$ & Sea: Lustre read data & Eq.~\ref{eq:msl} \\
       $D_{lw}$ & Sea: Lustre written data & Eq.~\ref{eq:msl} \\
       $D_{m}$ & Intermediate data & \ref{eq:msc} \\
       $D_{f}$ & Final output data & \\
       $F$ & File size & \\
       \hline
              \multicolumn{3}{|c|}{Bandwidths} \\                                         
       \hline                                                                      
       $B_{lr}$ & Perceived Lustre read bandwidth & Eq.~\ref{eq:lustrenpc}, \ref{eq:lustrepc}, \ref{eq:sea}, \ref{eq:msl}, \ref{eq:msc}\\
       $B_{lw}$ & Perceived Lustre write bandwidth & Eq.~\ref{eq:lustrenpc}, \ref{eq:msl}\\
       $B_{n}$ & Network bandwidth & \\              
       $B_{or}$ & Lustre OST read bandwidth & \\     
       $B_{ow}$ & Lustre OST write bandwidth & \\    
       $B_{mr}$ & Memory read bandwidth (same as for tmpfs) & Eq.\ref{eq:cache}, \ref{eq:mst}, \ref{eq:msc}\\
       $B_{mw}$ & Memory write bandwidth (same as for tmpfs) & Eq.~\ref{eq:cache}, \ref{eq:mst}, \ref{eq:msc}\\
       $B_{dr}$ & Local disk read bandwidth & Eq.~\ref{eq:msd}\\                   
       $B_{dw}$ & Local disk write bandwidth & Eq.~\ref{eq:msd}\\                  
       \hline                                                                      
       \multicolumn{3}{|c|}{Nodes} \\                                              
       \hline                                                                      
       $N_{c}$ & Number of compute nodes & Eq.~\ref{eq:cache}, \ref{eq:mst}, \ref{eq:msd}, \ref{eq:msc}\\
       $N_{d}$ & Number of data nodes & \\           
       $N_{t}$ & Number of threads per compute node & \\
       \hline                                                                      
       \multicolumn{3}{|c|}{Storage} \\                                            
       \hline                                                                      
       $O$ & Number of Lustre OSTs & \\              
       $d$ & Number of local disks & \\              
       $S_{t}$ & tmpfs storage space & \\
       $S_{d}$ & Local disk storage space & \\
       \hline                                                                      
      \end{tabular}                                                                
      \caption{Lustre and Sea model symbols}                                       
      \label{table:1}                                                              
      \end{table}

      To effectively be able to predict in which scenarios Sea will provide speedup
      over the baseline solution, we require a model. Since different parallel file
      systems may operate differently, our baseline model will be based on Lustre which
      is commonly used on HPC infrastructure.

      For data intensive use cases, the makespan models for both Lustre and Sea can be broken
      down into two components: The amount of time it takes read the data and the amount
      of time it takes to write the data. With more heterogeneous applications (some components
      are compute intensive whereas others are data intensive), a third component, comprising
      of compute time, can be added. Furthermore, latency make also play a significant role
      application makespan, particularly in scenarios with large amounts of small files.
      We choose to ignore latency costs in our model and make the assumption that the
      application bottleneck is the bandwidth, however, for more accurate estimates we
      might consider the addition of file system latency, as a fourth model component.

      A simplified version of the Lustre makespan model can be defined as follows:

      \begin{equation}\label{eq:lustrenpc}
          M_{l} =  \frac{D_{r}}{B_{lr}} + \frac{D_{w}}{B_{lw}}
      \end{equation}

      %\spacing{1}
      %Where, \\
      %$M_{l}$ is the Lustre makespan \\
      %$D_{r}$ is the amount of data read \\
      %$B_{r}$ is the read bandwidth \\
      %$D_{w}$ is the amount of data written \\
      %$B_{w}$ is the write bandwidth \\

      %\spacing{1.5}
      To determine the Lustre bandwidth, one must consider the three components involved:
  1) the network bandwidth of the compute nodes, 2) the network bandwidth of the data nodes,
  and 3) the collective bandwidth of the Lustre storage devices. Depending on each component's
  respective values, either of the three may be the source of a bottleneck. The
  Lustre bandwidth read and write models can therefore be described as follows:

      \begin{equation} %\label{eq:blr}
          B_{lr} = \min{(B_{n}N_{c}, B_{n}N_{d}, B_{or}\min{(O, N_{c}N_{t})})}
      \end{equation}

      and

      \begin{equation}%\label{eq:blw}
          B_{lw} = \min{(B_{n}N_{c}, B_{n}N_{d}, B_{ow}\min{(O, N_{c}N_{t})})}
      \end{equation}

      %\spacing{1}
      %Where, \\
      %$B_{lr}$ is the read bandwidth of Lustre \\
      %$B_{lw}$ is the write bandwidth of Lustre \\
      %$B_{or}$ is read bandwidth of the Lustre \gls{ost}s \\
      %$B_{ow}$ is the write bandwith of the Lustre \gls{ost}s\\
      %$B_{n}$ is the network bandwidth \\
      %$N_{c}$ is the number of compute nodes \\
      %$N_{d}$ is the number of data nodes \\
      %$n$ is the number of threads per compute node \\

      %\spacing{1.5}
      For the sake of simplicity, the above models assume that the network bandwidth
      between the compute nodes and data nodes is the same. This, however, may not
      necessarily be the case. Furthermore, the model also assumes that each file can
      only be located on a single OST, meaning that the parallel bandwidth can at maximum be
      as fast as all OSTs combined and as slow as the minimum number of compute threads
      reading and writing files.

      As with many file systems, page cache plays an important role in the speed of
      application read and writes in Lustre. Since the effect of page cache may be
      non-negligible given amount of memory available and the data accessed during the
      execution of the application, it is important to include it in our model. The makespan
      of an application I/O to and from page cache can be described as the following:
      Equation~\ref{eq:lustrenpc} where it is assumed that none of the data is written or read from page cache.

      \begin{equation}\label{eq:cache}
          M_{c} = \frac{D_{cr}}{B_{mr}N_{c}} + \frac{D_{cw}}{B_{mw}N_{c}}
      \end{equation}

      %\spacing{1}
      %Where, \\
      %$M_{c}$ is the makespan of writing to cache \\
      %$D_{cr}$ is the amount of data read from cache \\
      %$D_{cw}$ is the amount of data written to cache \\
      %$N_{c}$ is the number of compute nodes \\
      %$B_{mr}$ is the memory read bandwidth \\
      %$B_{mw}$ is the memory write bandwidth \\

      %\spacing{1.5}
       As each individual compute node has its own set of memory, we treat the total
      memory bandwidth as the sum of the individual memory bandwidth of each compute node.

      Page cache is difficult to summarize accurately and effectively within a model.
      For one, we must not only consider available memory and anonymous memory used by
      the application, but we must also consider which pages are candidates for eviction
      and which files they belong to. In addition, in the case of writes, we must consider
      asynchronous flushing and the throttling that may occur as a consequence of surpassing
      the \texttt{dirty\_ratio}. Furthermore, Lustre also has its own user-defined settings
      for how it interacts with the cache that would add additional complexities to the model.
      As a result, we assume two possible scenarios, one in which page cache is never used (Equation~\ref{eq:lustrenpc})
      and one in which all application I/O occurs within page cache with the exception of the
      first read which must occur on Lustre (Equation~\ref{eq:lustrepc}). These two models allow
      us to define the bounds of Lustre's performance.

      \begin{equation}\label{eq:lustrepc}
          M_{lc} = \frac{D_{I}}{B_{lr}} + M_{c}
      \end{equation}

      %\spacing{1}
      %Where, \\
      %$M_{lc}$ is the Lustre makespan with page cache \\
      %$D_{i}$ is the amount of input data \\
      %$B_{lr}$ is the Lustre bandwidth \\
      %$M_{c}$ is the makespan of the I/O to page cache \\

      %\spacing{1.5}
      Sea's model is more complex than Lustre's as there can be several
      layers of different devices. For instance, Sea's model can be defined as:

      \begin{equation}\label{eq:sea}
          M_{s} = \frac{D_{I}}{B_{lr}} + M_{1} + \cdots + M_{n}
      \end{equation}

      Here, $M_{n}$ represents the makespans of the different possible storage levels
      (e.g. tmpfs, NVMe, SSD, HDD, Lustre). For our model, we will assume 3 storage layers:
      1) fast tmpfs, 2) intermediate local SSD storage, and 3) slow parallel file system layer.

      Since the modelling of page cache is even more challenging with Sea due to the additional tmpfs
      and SSD layer, we will will model the upper and lower performance bounds, as we did with Lustre.
      Using the three layers and disregarding any possible effects of caching, we can redefine the
      Sea model to be:

      \begin{equation}\label{eq:snc}
          M_{s} = M_{sl} + M_{sd} + M_{st}
      \end{equation}

         Where $M_{sl}$ represents the Lustre component of the Sea makespan, and
      $M_{sd}$ and $M_{st}$ represent the disk and tmpfs component of the Sea
      makespan, respectively.

      The tmpfs component of the Sea makespan can be defined as the amount of
      data that can be written ($D_{tw}$) to and read ($D_{tr}$) from tmpfs
      over its respective bandwidths ($B_{mr}$ and $B_{mw}$). In other words:

      \begin{equation}\label{eq:mst}
          M_{st} = \frac{D_{tr}}{B_{mr}N_{c}} + \frac{D_{tw}}{B_{mw}N_{c}}
      \end{equation}

      \begin{equation*}\label{eq:dtr}
          D_{tr} = \min\left(D_{m}, \max{\left(N_{c}(S_{t} - FN_{t}), 0 \right)} \right)
      \end{equation*}
      \begin{equation*}\label{eq:dtw}
          D_{tw} = \min\left(D_{m} + D_{f}, \max{\left(N_{c}(S_{t} - FN_{t}), 0 \right)} \right)
      \end{equation*}

      In an optimal scenario all intermediate data ($D_{m}$) and final output
      data ($D_{f}$) would fit in tmpfs. This would provide an application using
      Sea in-memory performance. However, due to limited tmpfs storage space ($S_{t}$), it is unlikely to be the case. In addition, Sea may further restrict
      available storage space to prevent exceeding tmpfs storage by ensuring that
      there is at least sufficient space for $n$ threads to each write a file of
      size $F$.

      The local disk  makespan model is similar to the tmpfs makespan model, however, we
      must ensure to disregard any data that has already been written to tmpfs.
      Furthermore, in Sea, it is possible to leverage however many disk-based
      file systems are available for use ($d$). For our model, we assume that the
      size of each device is identical.
      The makespan model can be defined as follows:

      \begin{equation}\label{eq:msd}
          M_{sd} =  \frac{D_{dr}}{B_{dr}dN_{c}} + \frac{D_{dw}}{B_{dw}dN_{c}}
      \end{equation}

      \begin{equation*}\label{eq:ddr}
          D_{dr} = \min{(D_{m} - D_{tr}, \max{(N_{c}(S_{d}d - FN_{t}),0)})}
      \end{equation}

      \begin{equation*}\label{eq:ddw}
          D_{dw} = \min{(D_{m} + D_{f} - D_{tw}, \max{(N_{c}(S_{d}d - FN_{t}),0)})}
      \end{equation}

            The final component of the Sea model is the Lustre component (Eq.~\ref{eq:msl}). Sea's Lustre
      makespan model consists of the initial read from Lustre and includes and
      data that must be written to Lustre due to insufficient space on local
      storage and the makespan to read the intermediate data from Lustre.

      \begin{equation}\label{eq:msl}
          M_{sl} = \frac{D_{I}}{B_{lr}} + \frac{D_{lr}}{B_{lr}} + \frac{D_{lw}}{B_{lw}}
      \end{equation}
      \begin{equation*}\label{eq:dlr}
          D_{lr} = D_{m} - D_{dr} - D_{tr}
      \end{equation*}
      \begin{equation*}\label{eq:dlw}
          D_{lw} = D_{m} + D_{f} - D_{dw} - D_{tw}
      \end{equation*}

      Sea and Lustre have an identical lower bound. That is, ideally, both must
      perform the first read from Lustre, but all subsequent data accesses can
      be performed entirely within the page cache. The page cache model for Sea
      can be defined as the following:

      \begin{equation}\label{eq:msc}
          M_{sc} = \frac{D_{I}}{B_{lr}} + \frac{D_{m}}{B_{mr}N_{c}} + \frac{D_{m} + D_{f}}{B_{mw}N_{c}}
      \end{equation}
\subsection{Experiments}
\subsubsection{Pipelines}
      To evaluate the Lustre and Sea models defined in Section~\ref{model} and the real
      performance of both file systems with data intensive applications, we wrote a simple
      Python application based off of Algorithm~\ref{alg:incrementation}.          
      Using this application, we can easily control how much intermediate data is produced
      by altering the amount of iterations required. Although our model should be able
      to support images of different sizes, we wanted to minimize any possible     
      scheduling effects from our experiments. Therefore, each application         
      processes the same amount of input data and performs the same amount of computation.

      As with the experiments performed in Chapter~\ref{chp:eval}, we will use the BigBrain
      as a representative scientific datasets. For all our experiments, we utilize the
      \SI{20}{\micro\meter} dataset, which totals to approximately \SI{603}{\gibi\byte}.
      The dataset was broken down into 1000 files each consisting of \SI{617}{\mebi\byte}
      of data.

      We evaluate Sea using 4 different experimental conditions highlighted in Table~\ref{table:cond}:
      1) varying the number of nodes, 2) varying the number of disks, 3) varying the number of threads and 4)
      varying the number of iterations. Experimental condition 1 tests the effects 
      of increasing concurrent accesses to Lustre while fixing disk parallel threads. Condition 2
      varies disk contention while fixing contention to Lustre, whereas 3 tests the effects
      of contention on both Lustre and local storage. Experimental condition       
      4 varies the total amount of intermediate data produced by the application.
\subsubsection{Infrastructure}
\begin{table}
      \centering
      \begin{tabular}{@{}|c|c|c|c|c|@{}}
       \hline
       Condition & Nodes & Disks & Threads & Iterations \\
       \hline
       \multirow{5}{*}{\setword{1}{exp:nodes}} & 1 & 6 & 6 & 10 \\
       & 2 & 6 & 6 & 10 \\
       & 3 & 6 & 6 & 10 \\
       & 4 & 6 & 6 & 10 \\
       & 5 & 6 & 6 & 10 \\
       \hline
       \multirow{6}{*}{\setword{2}{exp:disks}} & 4 & 1 & 6 & 10 \\
       & 4 & 2 & 6 & 10 \\
       & 4 & 3 & 6 & 10 \\
       & 4 & 4 & 6 & 10 \\
       & 4 & 5 & 6 & 10 \\
       & 4 & 6 & 6 & 10 \\
       \hline
       \multirow{5}{*}{\setword{3}{exp:threads}} & 4 & 6 & 1 & 10 \\
       & 4 & 6 & 6 & 10 \\
       & 4 & 6 & 12 & 10 \\
       & 4 & 6 & 24 & 10 \\
       & 4 & 6 & 48 & 10 \\
       \hline
       \multirow{5}{*}{\setword{4}{exp:iterations}} & 4 & 6 & 6 & 1 \\
       & 4 & 6 & 6 & 5 \\
       & 4 & 6 & 6 & 10 \\
       & 4 & 6 & 6 & 15 \\
       & 4 & 6 & 6 & 20 \\
       \hline

      \end{tabular}
      \caption{Experimental conditions}
      \label{table:cond}
      \end{table}

      \begin{table}
      \centering
      \begin{tabular}{@{}|c|c|c|@{}}
       \hline
       Storage layer & Action & Average bandwidth (MiB/s) \\
              \hline
       \multirow{3}{*}{tmpfs} & read & 6676.48 \\
       & cached read & 6318.08  \\
       & write & 2560.00 \\
       \hline
       \multirow{3}{*}{local disk} & read & 501.70  \\
       & cached read & 7034.88 \\
       & write & 426.00 \\
       \hline
       \multirow{3}{*}{Lustre} & read & 1381.14 \\
       & cached read & 6103.04  \\
       & write & 121.00  \\

       \hline
